---
title: "Final Project"
author: "Andres Caso"
date: "28-07-2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
```

## Shiny App

This shiny app use the ChickWeight datasets to predict the weight of chicks based in the age and type of diet

The dataset have 4 variables:
     - weight: a numeric vector giving the body weight of the chick (gm).

     - Time: a numeric vector giving the number of days since birth when the 
     measurement was made.

     - Chick: an ordered factor with levels 18 < ... < 48 giving a unique 
     identifier for the chick. The ordering of the levels groups chicks on 
     the same diet together and orders them according to their final weight 
     (lightest to heaviest) within diet.

     - Diet: a factor with levels 1, ..., 4 indicating which experimental 
     diet the chick received.


## Shiny App

### Side Bar

In the side bar you can selected the days and type of diet of a chick

Type of diet: you have 4 options (1, 2, 3 and 4)

Age: You can select between 1 to 25 days of life

```{r sum}
summary(ChickWeight)
```

---

### Main Panel

In the main panel you can look 3 values

- the age and type of diet of the chick you selected in the side bar. 
- a graphic of the weights and age separated for the type of diet and a point with the predicted weight
- Value of predicted weight

```{r plot, fig.width=8, fig.height=3}
ggplot(data = ChickWeight, aes(Time, weight)) + geom_line(aes(color=Diet))
```

